---
title: "Codex Energy Drink"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(fig.path = "figures/", fig.ext = "png")  # Save all plots to 'figures/' folder
```

```{r}
setwd("C:/Users/Mideh/Desktop")
dim_cities <- read.csv("dim_cities.csv")
dim_repondents <- read.csv("dim_repondents.csv")
fact_survey_responses <- read.csv("fact_survey_responses.csv")

```



#### Visiualizing the data

```{r}
head(dim_cities)
```
```{r}
head(fact_survey_responses, 7)
```
```{r}
head(dim_repondents)
```


```{r}
# loadining necesaary libraies
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
```



```{r}
# joining all the data set to get derive insights
Joined <- dim_repondents %>%
  inner_join(fact_survey_responses) %>%
  inner_join(dim_cities)
```
#### Gender that prefer Energy drink more
```{r}
# count of who prefer energy drink more
#grouping by gender and consume_frequency to analyze preference
Pref <- Joined %>%
group_by(Gender, Consume_frequency) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

#visualizing the preference
ggplot(Pref, aes(x = "Consume_frequency", y = count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Preference of Energy drink", x= "Consume_frequency", y = "count") +
  theme_minimal()
```
#### Age group that prefers energy drink more 

```{r}
Age_pref <- Joined %>%
  group_by(Age, Consume_frequency) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#visualizing the Age preference
ggplot(Age_pref, aes(x = "Consume_frequency", y = count, fill = Age)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Age Preference of Energy drink", x= "Consume_frequency", y = "Age_count") +
  theme_minimal()
```

#### Preferred Market Channel by youth
```{r}
#filtering the ages between 15-30
Youth_marketing <- Joined %>%
  filter(Age >= 15 & Age <= 30) %>%
  select(Marketing_channels)

#type of market channel preferred by youth 
Market_channel_count <- Youth_marketing %>%
  group_by(Marketing_channels) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

#visualizing the type of market channel preferred
ggplot(Market_channel_count, aes(x = "Age", y = count, fill = Marketing_channels)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Market channel that reaches the most youth", x= "Market_channel", y = "Age_count") +
  theme_minimal()
```

```{r}
#checking fore the most preferred ingredient energy drinks
Preferred_ingridients <- Joined %>%
  group_by(Ingredients_expected) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

#visualizing the preferred_ingredients 
ggplot(Preferred_ingridients, aes(x = "", y = count, fill = Ingredients_expected)) +
  geom_col() +
  coord_polar(theta = "y") +
  geom_label(aes(label = paste0(Ingredients_expected, "\n", count)), 
             position = position_stack(vjust = 0.5)) +
  labs(
    title = "Pie chart of the preferred ingredients by respondents",
    x = "",
    y = ""
  ) +
  theme_void()

```
#### Prefrered Ingridients
```{r}
# Packaging Preference 
Packaging_Pref <- Joined %>%
  group_by(Packaging_preference) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
# Visualizing the packaging_preference uisng a bar chart
ggplot(Packaging_Pref, aes(x = "Packaging_preference", y = count, fill = Packaging_preference)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Most preferred packaging ", x= "Packaging_preference", y = "count") +
  theme_minimal()
```
#### Current market leaders
```{r}
Market_leaders <- Joined %>%
  group_by(Current_brands) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#visualizing the current market leaders with a pie chart
ggplot(Market_leaders, aes(x = "", y = count, fill = Current_brands)) +
  geom_col() +
  coord_polar(theta = "y") +
  geom_label(aes(label = paste0( count)), 
             position = position_stack(vjust = 0.5)) +
  labs(
    title = "Pie chart showing the current market leaders by respondents",
    x = "",
    y = ""
  ) +
  theme_void()
```
#### Reasons for choosing brands
```{r}
Reasons <- Joined %>%
  group_by(Reasons_for_choosing_brands) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#visualizing the output of the reasons
ggplot(Reasons, aes(x = "Reasons_for_choosing_brands", y = count, fill =Reasons_for_choosing_brands )) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Reasons why the brands are being chosen by respondents ", x= "reasons", y = "count") +
  theme_minimal()
```
#### Most effective market channels
```{r}
#marketing channels to reach more customers
M_C <- Joined %>%
  group_by(Marketing_channels) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
# visualizing 
ggplot(M_C, aes(x = Marketing_channels, y = count, fill = Marketing_channels )) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Most effective marketing channels ", x= "Marketing_channels", y = "count") +
  theme_minimal()
```

####
```{r}
# checking if the market channels have been effective 
Adult_marketing <- Joined %>%
  filter(Age >= 31 & Age <= 65) %>%
  select(Marketing_channels)

#type of market channel preferred by Adult
Market_channel_count2 <- Adult_marketing %>%
  group_by(Marketing_channels) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#visualizing
ggplot(Market_channel_count2, aes(x = Marketing_channels, y = count, fill = Marketing_channels)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Market channel that reaches Adults", x= "Market_channel", y = "count") +
  theme_minimal()
```
#### Brands Perception
```{r}
Brand_p <- Joined %>%
  group_by(Brand_perception) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
  # visualizing brand_perception using bar chart
ggplot(Brand_p, aes(x= Brand_perception, y = count, fill = Brand_perception)) +
  geom_bar(stat = "identity", position = "dodge") + labs(title = "Respondents view on brand", x = "Brand_Perception", y= "count")
  
```
#### Cities to focus on
```{r}
Cities <- Joined %>%
  group_by(City) %>%
  summarise(count = n()) %>%
  arrange((count))
#visualizing cities with bar chart
ggplot(Cities, aes(x = City, y = count, fill = City)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Cities", x = "City", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#### Respondents Prefrered Purchase Outlets
```{r}
#where respondents prefer to purchase Energy drinks
Purchased_pref <- Joined %>%
  group_by(Purchase_location) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
# visualizing purchased_pref
ggplot(Purchased_pref, aes(x = Purchase_location, y = count, fill = Purchase_location)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "preferred location for getting energy drinks", x = "Purchase_location", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
```
#### Typical Consumption patterns
```{r}
#Typical consumption situations
Consumption_situation <- Joined %>%
  group_by(Typical_consumption_situations) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#visualizing
ggplot(Consumption_situation, aes(x =Typical_consumption_situations , y = count, fill = Typical_consumption_situations)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Typical consumption situations of respondents", x = "Typical_consumption_situations", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
#### Factors influencing purchase decisions 
```{r}
# Example of selecting relevant columns for analysis
Influencing_factors <- Joined %>%
  select(Price_range, Limited_edition_packaging)
  # Summary of price range and packaging by purchase decision


ggplot(Influencing_factors, aes(x = Price_range, fill = Limited_edition_packaging)) +
  geom_bar(position = "dodge") +
  labs(title = "Purchase Decision by Price Range", x = "Price Range", y = "Count")
```
